\documentclass[11pt,oneside]{article}

% All packages/macros live here:
\input{other_tex/format_macros.tex}

% Optional math + theorem layers (safe if absent/empty)
\IfFileExists{other_tex/math.tex}{\input{other_tex/math.tex}}{}
\IfFileExists{other_tex/theorems.tex}{\input{other_tex/theorems.tex}}{}

% -------------
% Metadata
% -------------
\title{\PaperTitleMain}
\ifdefined\Authors
  \author{\Authors}
\else\ifdefined\AuthorName
  \author{\AuthorName}
\else
  \author{Author Name}
\fi\fi
\date{\today}

\begin{document}
\maketitle

% Dedication inline under the title (no page break)
\IfFileExists{other_tex/dedication.tex}{%
  \vspace{0.75\baselineskip}\input{other_tex/dedication.tex}%
}{}

% Abstract on its own page
\clearpage
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}
\input{other_tex/abstract.tex}

% ----------------
% Notation (added)
% ----------------
\section*{Notation}
\addcontentsline{toc}{section}{Notation}
\noindent
\begin{tabular}{@{}ll}
$c$ & hop-cap (front) speed; exact in SI.\\
$\hbar$ & phase quantum; exact in SI.\\
$e$ & elementary charge; exact in SI.\\
$\alpha$ & fine-structure constant (dimensionless EM coupling).\\
$\epsilon_0,\ \mu_0$ & vacuum permittivity/permeability (derived: $c^{-2}=\mu_0\epsilon_0$).\\
$Z_0$ & vacuum impedance $=\mu_0 c \approx 376.730~\Omega$.\\
$R_K$ & quantum of resistance $=h/e^2 \approx 25{,}812.807~\Omega$.\\
$\mathcal Q_{\max}$ & reference stitch capacity $=\hbar c$ (J$\cdot$m).\\
$\mathcal Q_{\rm EM}$ & EM share of the stitch capacity.\\
$\varphi$ & electrostatic potential; $\phi$ reserved for generic phase.\\
$R_H,\ R_\infty$ & Rydberg constants for H and infinite-mass nucleus.\\
\end{tabular}

\section{Charge and the Fine-Structure Constant as Stitch--Capacity Ratios}
\textit{From Dimensionless Mystery to Hydrogen's Signature}

\subsection*{Scope}
We extend the S/t principle to electromagnetism. The elementary charge $e$ and the fine-structure constant
\begin{equation}
\alpha \;=\; \frac{e^2}{4\pi\epsilon_0\hbar c} \;\approx\; \frac{1}{137}
\end{equation}
are recast as \emph{stitch--capacity ratios}: the U(1) (electromagnetic) share of a universal reference throughput $\mathcal Q_{\max}=\hbar c$ (units J$\cdot$m = action$\times$speed). Concretely,
\begin{equation}
\alpha \;=\; \frac{\mathcal Q_{\rm EM}}{\mathcal Q_{\max}},
\end{equation}
and $e$ represents the minimal quantized packet of that fractional flow (numerically tied to CODATA \cite{tiesinga2021codata}). Hydrogen then becomes the first precision test-bed: $\alpha$ fixes the speed scale $v/c=\alpha$, gross line positions, and fine-structure patterns.

\paragraph{Notation guard.}
We reserve $\mathcal Q$ for \emph{channel throughput capacity} (J$\cdot$m). This is distinct from heat $Q$ (energy transfer) and electric charge $q$. Electrostatic potential is written $\varphi$ to avoid collision with phase $\phi$.

\subsection{Stitch--Capacity View of Charge and \texorpdfstring{$\alpha$}{alpha}}

\paragraph{Reference throughput (identity).}
Each stitch admits a natural reference capacity
\begin{equation}
\mathcal Q_{\max}\;=\;\hbar c.
\end{equation}
SI identities link the constants by
\begin{equation}
e^2 \;=\; 4\pi\epsilon_0\,\alpha\,\hbar c,
\end{equation}
so given $(e,\hbar,c)$ and a measured $\alpha$, $\epsilon_0$ follows consistently \cite{bipm2019si,tiesinga2021codata}. Equivalently, match a vacuum ratio to a matter normalization:
\begin{equation}
\alpha \;=\; \frac{e^2}{4\pi\epsilon_0\hbar c}
\;=\; \frac{Z_0}{2 R_K},
\qquad
Z_0=\mu_0 c,\ \ \ R_K=\frac{h}{e^2}.
\end{equation}

\paragraph{Fractional use (capacity partition).}
The EM channel occupies a fraction $\alpha$ of $\mathcal Q_{\max}$:
\begin{equation}
\alpha \;=\; \frac{\mathcal Q_{\rm EM}}{\mathcal Q_{\max}}, \qquad
0\le \alpha(\mu)\le 1,\qquad \sum_c \alpha_c(\mu)\le 1,
\end{equation}
with mild scale dependence $\alpha(\mu)$ (``running'').

\paragraph{Elementary charge (packet).}
Solving the SI identity yields
\begin{equation}
e \;=\; \sqrt{4\pi\epsilon_0\,\alpha\,\hbar c},
\end{equation}
so the observed charge quantum corresponds to one minimal packet of the EM channel's fractional throughput (with $e$ exact in the modern SI; $\alpha$ determined from experiment) \cite{bipm2019si,tiesinga2021codata}.

\paragraph{Bias-field link (Coulomb).}
For a point proton at the origin, the scalar potential and field are
\begin{equation}
\varphi(r)=\frac{k_C\,e}{r},\qquad k_C=\frac{1}{4\pi\epsilon_0},\qquad
\mathbf E=-\nabla\varphi.
\end{equation}
The electron’s potential energy in this field is
\begin{equation}
U(r)=-\,e\,\varphi(r)=-\frac{k_C\,e^2}{r},
\end{equation}
which yields the attractive force $\mathbf F=-\nabla U=-\,e\,\mathbf E$.
This is the U(1) instance of a conservative-bias template \cite{coulomb1785,griffiths2013electrodynamics}.

\paragraph{Microcell heuristic (operational, testable).}
Near-isotropic adjacency suggests coarse angular addressability into $N$ microcells per tick. If a U(1) on/off event occupies exactly one cell with probability
\begin{equation}
p_{\rm on} \;=\; \frac{1}{N},
\end{equation}
the \emph{capacity fraction} identification becomes
\begin{equation}
\alpha \;\approx\; \frac{1}{N}, \qquad N\;=\;\alpha^{-1}.
\end{equation}
At low energy, $\alpha^{-1}\!\approx\!137.036\Rightarrow N\!\approx\!137$. As the scale $\mu$ increases, $\alpha$ grows slowly and the effective $N$ decreases (running). \emph{Falsifier:} cross-platform determinations of $\alpha$ at the same $\mu$ (recoil, QED \(g\!-\!2\), quantum Hall) that imply inconsistent $N$.

\paragraph{Phase-toggle version (natural units).}
Equivalently, let the minimal U(1) phase increment be $\delta\phi$ (gauge coupling $g=\delta\phi$ in $\hbar=c=1$). Then
\begin{equation}
\alpha \;=\; \frac{g^2}{4\pi} \;=\; \frac{(\delta\phi)^2}{4\pi}
\quad\Rightarrow\quad
\delta\phi \;=\; \sqrt{\frac{4\pi}{N}} \;\approx\; 0.303~\text{rad}\ \ (\sim 17^\circ)\ \text{for } N\!\approx\!137.
\end{equation}

\paragraph{SI anchor (metrological status).}
Since 2019, $e$ and $h$ are exact SI defining constants; $c$ is exact; $\alpha$ is measured. The relation $e^2=4\pi\epsilon_0\alpha\hbar c$ then ties $\epsilon_0$ and $\mu_0$ through $c^{-2}=\mu_0\epsilon_0$ and $Z_0=\mu_0 c$ \cite{bipm2019si,tiesinga2021codata}. Experimentally, $Z_0$ is read from free-space wave ratios and $R_K$ from the quantum Hall effect, so $\alpha=Z_0/(2R_K)$ is overconstrained. Numerically, $Z_0 \approx 376.730~\Omega$ and $R_K \approx 25{,}812.807~\Omega$, giving $\alpha \approx Z_0/(2R_K)\approx 1/137.036$.

\subsection{Hydrogen: \texorpdfstring{$\alpha$}{alpha} in Action (Rydberg, Lines, Speeds)}

\paragraph{Reduced mass and levels.}
For hydrogen use
\begin{equation}
\mu \;=\; \frac{m_e m_p}{m_e+m_p} \;\approx\; m_e\,(1-5.4\times 10^{-4}),
\end{equation}
with bound-state energies and constants
\begin{equation}
E_n \;=\; -\,\frac{\mu c^2 \alpha^2}{2 n^2},\qquad
R_H \;=\; \frac{\mu c \alpha^2}{2h},\qquad
R_\infty \;=\; \frac{m_e c \alpha^2}{2h},
\end{equation}
and $R_H=(\mu/m_e)\,R_\infty$ \cite{griffiths2018quantum}.

\paragraph{Bohr speed and length (one-liners).}
Angular-momentum quantization with Coulomb balance gives
\begin{equation}
\frac{v}{c} \;=\; \alpha \quad (n=1), \qquad
a_0 \;=\; \frac{4\pi\epsilon_0\,\hbar^2}{\mu e^2} \;=\; \frac{\hbar}{\mu c\,\alpha}.
\end{equation}

\paragraph{Balmer-$\alpha$ (visible red) and Lyman-$\alpha$ (UV).}
\begin{equation}
\frac{1}{\lambda_{\rm H\alpha}} \;=\; R_H\!\left(\frac{1}{2^2}-\frac{1}{3^2}\right)\ \Rightarrow\ \lambda_{\rm H\alpha}\approx 656~\mathrm{nm},
\end{equation}
\begin{equation}
\frac{1}{\lambda_{\rm Ly\alpha}} \;=\; R_H\!\left(1-\frac{1}{2^2}\right)=\tfrac{3}{4}R_H\ \Rightarrow\ \lambda_{\rm Ly\alpha}\approx 121.6~\mathrm{nm},
\end{equation}
both directly controlled by $\alpha$ through $R_H$ \cite{rydberg1890,fowler1922hydrogen}. Using CODATA $R_\infty$, predicted line positions match spectroscopy within the usual reduced-mass and QED corrections.

\paragraph{Fine structure and QED (foreshadow).}
Relativistic and spin--orbit corrections split levels by $\sim \alpha^4 m_e c^2$ (with $n,j$ dependence), while the Lamb shift adds higher-order QED terms; all scale with powers of $\alpha$ and match precision spectroscopy \cite{dirac1930principles,bethe1947lamb,griffiths2018quantum}.

\subsection{Running and Cross-Checks}

\paragraph{One-loop slope (target).}
For one light Dirac fermion,
\begin{equation}
\frac{d\alpha}{d\ln\mu} \;\approx\; \frac{2}{3\pi}\,\alpha^2.
\end{equation}
With multiple light charged fermions,
\begin{equation}
\frac{d\alpha}{d\ln\mu} \;\approx\; \frac{2}{3\pi}\!\left(\sum_f Q_f^2\right)\alpha^2 \;+\; \cdots,
\end{equation}
and hadronic vacuum polarization matters at low energies.

\paragraph{Consistency tests (falsifiers).}
\begin{itemize}
  \item \textbf{Hydrogen metrology:} $R_H$ from multiple lines vs.\ $\alpha$ from recoil/QED \(g\!-\!2\)/quantum Hall must agree after reduced-mass and known QED corrections \cite{griffiths2018quantum,tiesinga2021codata}.
  \item \textbf{Platform concordance:} Disagreement of $\alpha$ beyond uncertainties falsifies the capacity-fraction identification.
  \item \textbf{Running check:} $\alpha(\mu)$ must track the known slope (with thresholds); gross departures would contradict the microcell/running picture.
\end{itemize}

\paragraph{Constants cross-link.}
Once $(e,h,c,\alpha)$ are fixed/measured, $\epsilon_0$ and $\mu_0$ follow via $c^{-2}=\mu_0\epsilon_0$ and $Z_0=\mu_0 c$; $\alpha$ controls hydrogenic spectra, $Z_0$ controls EM wave ratios, and all are mutually consistent \cite{bipm2019si,tiesinga2021codata}.

\subsection*{Interpretation and Theme}
\begin{itemize}
  \item $\alpha$ is the EM share of the universal stitch capacity $\mathcal Q_{\max}=\hbar c$.
  \item The ``smallness'' $\alpha\!\approx\!1/137$ reflects rare activation among $N\!\approx\!137$ microcells (heuristic, testable).
  \item The U(1) toggle is a minimal phase $\delta\phi\!\approx\!0.30$ rad in natural units.
  \item $e$ is the quantized packet of this fractional flow in SI.
  \item Hydrogen's $v/c=\alpha$, $a_0$, and lines (Balmer/Lyman, fine structure) are direct readouts of $\alpha$ \cite{bohr1913constitution,griffiths2018quantum}.
\end{itemize}

\subsection*{Summary box}
\begin{center}
\setlength{\fboxsep}{8pt}%
\setlength{\fboxrule}{0.8pt}%
\fbox{%
  \begin{minipage}{0.95\linewidth}\small\raggedright
  $\alpha = \mathcal Q_{\rm EM}/\mathcal Q_{\max}$, $\mathcal Q_{\max}=\hbar c$, $e^2=4\pi\epsilon_0\,\alpha\,\hbar c$~\cite{bipm2019si,tiesinga2021codata}.\\[4pt]
  \textbf{Heuristic addressability:} $N=\alpha^{-1}\approx 137$, $\delta\phi=\sqrt{4\pi/N}\approx 0.303~\mathrm{rad}$ ($\hbar=c=1$ here).\\[4pt]
  $\varphi(r)=k_C e/r$, $k_C=1/(4\pi\epsilon_0)$, $\mathbf E=-\nabla\varphi$, $U(r)=-e\,\varphi(r)=-k_C e^2/r$~\cite{coulomb1785,griffiths2013electrodynamics}.\\[4pt]
  \textbf{Hydrogen:} $E_n=-\,\mu c^2\alpha^2/(2n^2)$,\; $R_H=\mu c\alpha^2/(2h)$,\; $R_\infty=m_e c\alpha^2/(2h)$,\; $v/c=\alpha$ ($n=1$).\\[4pt]
  \textbf{Lines:} $\lambda_{\rm H\alpha}\approx 656~\mathrm{nm}$,\; $\lambda_{\rm Ly\alpha}\approx 121.6~\mathrm{nm}$~\cite{rydberg1890,fowler1922hydrogen}.\\[4pt]
  \textbf{Fine structure:} splittings $\sim \alpha^4 m_e c^2$ (with $n,j$);\; Lamb/QED corrections~\cite{dirac1930principles,bethe1947lamb}.
  \end{minipage}%
}
\end{center}

% Acknowledgments
\clearpage
%\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}
\IfFileExists{other_tex/acknowledgments.tex}{\input{other_tex/acknowledgments.tex}}{}

% Statements & housekeeping (each optional)
\section*{Competing interests}
\IfFileExists{other_tex/competing_interests.tex}{\input{other_tex/competing_interests.tex}}{}

\section*{Author contributions}
\IfFileExists{other_tex/authors_contributions.tex}{\input{other_tex/authors_contributions.tex}}{}

\section*{Funding}
\IfFileExists{other_tex/funding.tex}{\input{other_tex/funding.tex}}{}

\section*{Data and materials availability}
\IfFileExists{data_accessibility.tex}{\input{data_accessibility.tex}}{No new data were generated.}

\section*{Disclosure}
\IfFileExists{other_tex/disclosure.tex}{\input{other_tex/disclosure.tex}}{}

% ToC (after statements)
%\clearpage
%\tableofcontents

% Optional lists (simple boolean; no ifboolexpr)
%\clearpage
%\ifShowLists
%  \listoffigures
%  \listoftables
%\fi

% ----------------
% Glossary (optional; prints only if glossaries is loaded)
% ----------------
\IfGlossariesEnabled{
  %\clearpage
  \printglossary[title=Glossary]
}

% ----------------
% Bibliography (BibTeX by default)
% ----------------
\clearpage
\nocite{*} % avoid Empty thebibliography even with zero explicit \cite
\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}
